Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-06-10 analysis/sim/run_simpw.Rmd
refine sims
update sim
fig

SIMS=1000
#run 500 sims
FRAC_DE=0.05
FC=1
N_REPS=3
DGE_FUNC="deseq2"
SUM_COUNT=2e7
VARIANCE=c(0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,1.1,1.2,1.3,1.4,1.5)

@@

png("fig3_sim.png",width=720, height=480)
par(mar=c(c(5.1, 5.1, 2.1, 2.1) ))
par(mfrow=c(1,3))

>>>>

SIMS=1000
#run 500 sims
FRAC_DE=0.05
FC=1
N_REPS=3
DGE_FUNC="deseq2"
SUM_COUNT=2e7
VARIANCE=c(0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)

@@

png("fig3_sim.png", width=7,height=5,units="in",res=150,pointsize=12)
par(mar=c(c(5.1, 5.1, 2.1, 2.1) ))
par(mfrow=c(1,3))
